### 2019-02-21 paper_02_fluidsim/article.tex
Subsection -> paragraphbf sed -i 's/subsubsection/paragraphbf/g' */article.tex

\subsubsection{Balance between runtime efficiency and cost of development}
In today's world where clusters are moving from petascale to exascale
performance, computing power is aplenty. In most research scenarios, it becomes
apparent that \emph{man-hours are more expensive than computing time}. In other
words, the cost of development outweighs the cost of computing time. Therefore,
developers should be willing to make small sacrifices in efficiency, to improve
development time, code maintainability and clarity in general. In exceptional
cases when computing time become more expensive, one can still use
existing optimized and performance-tuned compiled libraries implemented in
native languages as the core, and rely on high level programming languages to
extend them for specific applications\footnote{See
  \citet{ramachandran_pysph_2016} for a similar discussion}.

@@

\subsubsection{Target audiences}
\fluidpack{sim} is designed to cater to the needs of three kinds of audience.
\begin{itemize}
\item \emph{Users}, who run simulations with already available solvers. To do
this, one needs to have very basic skills in Python scripting.
\item \emph{Advanced users}, who may extend \fluidpack{sim} by developing
customized solvers for new problems by taking advantage of built-in operators and
time-stepping classes.  In practice, one can easily implement such solvers by
changing a few methods in base solver classes.  To do this, one needs to have
fairly good skills in Python and especially object-oriented programming.
\item \emph{Developers}, who develop the base classes, in particular, the
operators and time stepping classes.  One may also sometime need to write compiled
extensions to improve runtime performance. To do this, desirable traits include
good knowledge in Python, \Numpy, \pack{Cython} and \pack{Pythran}.
\end{itemize}

@@

\subsubsection{Package organization}

@@

\subsubsection{The simulation object}

@@

\subsubsection{Profiling}

@@

\subsubsection{Scalability}

@@

\subsubsection{2D benchmarks}\label{sec:bench2d}

@@

\subsubsection{3D benchmarks}

>>>>

\paragraphbf{Balance between runtime efficiency and cost of development}
In today's world where clusters are moving from petascale to exascale
performance, computing power is aplenty. In most research scenarios, it becomes
apparent that \emph{man-hours are more expensive than computing time}. In other
words, the cost of development outweighs the cost of computing time. Therefore,
developers should be willing to make small sacrifices in efficiency, to improve
development time, code maintainability and clarity in general. In exceptional
cases when computing time become more expensive, one can still use
existing optimized and performance-tuned compiled libraries implemented in
native languages as the core, and rely on high level programming languages to
extend them for specific applications\footnote{See
  \citet{ramachandran_pysph_2016} for a similar discussion}.

@@

\paragraphbf{Target audiences}
\fluidpack{sim} is designed to cater to the needs of three kinds of audience.
\begin{itemize}
\item \emph{Users}, who run simulations with already available solvers. To do
this, one needs to have very basic skills in Python scripting.
\item \emph{Advanced users}, who may extend \fluidpack{sim} by developing
customized solvers for new problems by taking advantage of built-in operators and
time-stepping classes.  In practice, one can easily implement such solvers by
changing a few methods in base solver classes.  To do this, one needs to have
fairly good skills in Python and especially object-oriented programming.
\item \emph{Developers}, who develop the base classes, in particular, the
operators and time stepping classes.  One may also sometime need to write compiled
extensions to improve runtime performance. To do this, desirable traits include
good knowledge in Python, \Numpy, \pack{Cython} and \pack{Pythran}.
\end{itemize}

@@

\paragraphbf{Package organization}

@@

\paragraphbf{The simulation object}

@@

\paragraphbf{Profiling}

@@

\paragraphbf{Scalability}

@@

\paragraphbf{2D benchmarks}\label{sec:bench2d}

@@

\paragraphbf{3D benchmarks}
